resistanceModelNotesAndy

### 2015-07-21 resistanceModelNotesAndy.Rmd
notes

initial tree looks promising :
for mix1 better than sequential:
phi.SS2_0B < 0.66
phi.SS1_AO < 0.68
P_2 > 0.033

@@

@@

1. try to get some simple trees

1. decide how to format table of results
1. put some results together for Ian, not sure how to do trees
1. include a couple of contrasting graphs, to make a story. e.g. one where mixture better and one where sequential. Maybe number points on the figs.

1. it might be that the tyree results are not useful ??

1. sort order of insecticides for sequential figures

1. work out what to do if critical threshold not reached in findResistancePoints()
causes : Error in plot.window(...) : need finite 'xlim' values

1. review how to answer these questions.
Main question is : Tree1 is mixture better (0/1), Tree2 is mixture better by >20%.

@@

### suggestion from Beth
could provide a .csv file with the Curtis scenarios set up
and then the need to set the calibration number and params.csv in the R script can be removed altogether

### How best to refactor variables to arrays ?
Refactoring to arrays will reduce code volume, reduce risk of mistyped variable names and allow objects to be passed between functions.
cis/trans makes it slightly tricky, but not all variables have cis/trans
only used for genotype frequencies (f) and in output matrices fitness & genotype 
in the wild in Beths code :
```
fs.m.RS1RS2_cis <- f.m.RS1RS2_cis
fs.m.RS1RS2_trans <- f.m.RS1RS2_trans
```

>>>>

initial tree looks promising :
for mix1 better than sequential:
phi.SS2_0B < 0.66
phi.SS1_AO < 0.68
P_2 > 0.033
P_1

@@

** 14/7/15 **

putting results document together.

Just checking that the results file for the 1000 runs looks like the figures & UI for the 100 runs

run3: sequential best (seq 28+29, mix3 50)
run4: mixture best (seq 93+32, mix3 172)
run5: resistance to one in mixture develops more slowly than both in sequence (seq 29+103, mix1 152)

resistPointsI1[,1:5]
           [,1] [,2] [,3] [,4] [,5]
gen_cP0.1    38  999   11   57    7
gen_cP0.25   48  999   21   82   22
gen_cP0.5    53  999   28   93   29
resistPointsI2[,1:5]
           [,1] [,2] [,3] [,4] [,5]
gen_cP0.1    64  210    7    4   91
gen_cP0.25   90  250   21   21   99
gen_cP0.5   102  268   29   32  103
resistPointsMix1[,1:5]
           [,1] [,2] [,3] [,4] [,5]
gen_cP0.1    75  999    9   10   34
gen_cP0.25   93  999   30   57  116
gen_cP0.5   102  999   41   86  152
resistPointsMix3[,1:5]
           [,1] [,2] [,3] [,4] [,5]
gen_cP0.1   168  999   21  129  191
gen_cP0.25  199  999   38  159  202
gen_cP0.5   213  999   50  172  207

Now can I do the 20% better results ? 
 betterMix1Seq20_cP0.1 betterMix1Seq20_cP0.25  betterMix1Seq20_cP0.5 
                 0.136                  0.175                  0.173 
 betterMix2Seq20_cP0.1 betterMix2Seq20_cP0.25  betterMix2Seq20_cP0.5 
                 0.241                  0.326                  0.313 
 betterMix3Seq20_cP0.1 betterMix3Seq20_cP0.25  betterMix3Seq20_cP0.5 
                 0.672                  0.560                  0.488

rounded
 betterMix1Seq20_cP0.1 betterMix1Seq20_cP0.25  betterMix1Seq20_cP0.5 
                 0.14                  0.18                  0.17 
 betterMix2Seq20_cP0.1 betterMix2Seq20_cP0.25  betterMix2Seq20_cP0.5 
                 0.24                  0.33                  0.31 
 betterMix3Seq20_cP0.1 betterMix3Seq20_cP0.25  betterMix3Seq20_cP0.5 
                 0.67                  0.56                  0.49

Low phi values lead to sequential being better.
e.g. https://andysouth.shinyapps.io/shinyMixSeqCompare1 
runs 
3: phi 0.53, 0.79
19: phi 0.65, 0.44
25: phi 0.60, 0.56

** 15/7/15 **

installed triangle package
this to generate random deviates
rtriangle(n, a=0, b=1, c=(a+b)/2)

changed label 'combination' to 'mixture' in my generic curtis fig2 plot

** 16/7/15 **
reran 1000 sensitivity scenarios with new agreed input ranges
& reran 100 scenarios and put them into shinyMixSeqCompare1

check that the example runs still support the args the way they did before

the 3 example plots that I pasted into the word doc seem to be identical to what they were before
ARSE is it possible I didn't reload the package so that it used the old function version with the old input ranges ?

yes I think that's what I did !

rereran 100 runs and put them into shinyMixSeqCompare1

sorted order of insecticides for sequential figures

run shinyMixSeqCompare1 in a window rather than the browser to enable copy and pasting figures into word doc

copied 3 figs into the word doc. Note that run 9 is interesting. Mixture does much better than sequential.

@@

1. set 1000 runs to do tonight

1. redo the word results doc

@@

### refactoring variables to arrays ?
Refactoring to arrays will reduce code volume, reduce risk of mistyped variable names and allow objects to be passed between functions.
cis/trans makes it slightly tricky, but not all variables have cis/trans
only used for genotype frequencies (f) and in output matrices fitness & genotype 
in the wild in Beths code :
```
fs.m.RS1RS2_cis <- f.m.RS1RS2_cis
fs.m.RS1RS2_trans <- f.m.RS1RS2_trans
```
